Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia

### 2019-05-13 code/paper.Rmd
thinking about the talk pages

tidy_talk <- 
enframe(unlist(wh_wiki_talk_pages)) %>% 
  mutate(clean_text = str_remove_all(value, "\n|\t")) %>% 
  unnest_tokens(word, clean_text) %>% 
  anti_join(stop_words) %>% 
  filter(!word %in% c("article", "page", "talk", "utc", 
                      "class", "edit", "project's",
                      "importance", "rated", "wikiproject",
                      "project", "article", "articles", "article's",
                      "wikipedia", "start", "scale", 
                      "world", "heritage", "sites",
                      "links", "http", "parser", 
                      "output", "mw", "https",
                      "unsigned", "comment")) %>% 
  filter(!str_detect(word, "[[:digit:]]+")) %>% 
  filter(!str_detect(word, ":")) %>% 
  filter(!str_detect(word, "articles")) %>% 
  filter(!str_detect(word, "jump")) %>% 
  filter(!str_detect(word, "\\."))

@@

>>>>

tidy_talk_raw <- 
enframe(unlist(wh_wiki_talk_pages)) %>% 
  bind_cols(wh_wiki_table)

write.csv(tidy_talk_raw$value , "data/wh_wiki_talk_page_text.txt")

tidy_talk <- 
  tidy_talk_raw %>% 
    mutate(clean_text = str_remove_all(value, "\n|\t")) %>% 
  unnest_tokens(word, clean_text) %>% 
  anti_join(stop_words) %>% 
  filter(!word %in% c("article", "page", "talk", "utc", 
                      "class", "edit", "project's",
                      "importance", "rated", "wikiproject",
                      "project", "article", "articles", "article's",
                      "wikipedia", "start", "scale", 
                      "world", "heritage", "sites",
                      "links", "http", "parser", 
                      "output", "mw", "https",
                      "unsigned", "comment")) %>% 
  filter(!str_detect(word, "[[:digit:]]+")) %>% 
  filter(!str_detect(word, ":")) %>% 
  filter(!str_detect(word, "articles")) %>% 
  filter(!str_detect(word, "jump")) %>% 
  filter(!str_detect(word, "\\."))

# check which sites have some words
tidy_talk %>% 
  filter(word == "unesco") %>% 
  group_by(Site) %>% 
  tally(sort = T)

@@

# reload data
